### 2020-04-13 introduction.tex
Completed first draft of Chapters 1-4 for review

In this thesis, we demonstrate the coupled multiphysics modeling capabilities
of Moltres through the reference configuration of the MSFR design. Moltres
employs fully implicit coupling between the neutronics and thermal-hydraulics
governing equations, to fully account for the tight coupling expected in MSRs
due to the movement of fuel in the salt. We implemented flow using the
Navier-Stokes equations for an accurate representation of the flow profile as
opposed to imposing a predetermined velocity field.

The objectives of this thesis are: 1) study the steady-state operating
conditions with the reference \gls{MSFR} model, 2) study the transient
behavior of the \gls{MSFR} under several unprotected accident scenarios, and
identify general characteristic behaviors in MSRs and fast spectrum reactors.
The simulation results are verified against the results by Fiorina et al.
\cite{fiorina_modelling_2014} and Aufiero et al.
\cite{aufiero_development_2014}.

** insert thesis outline here **

>>>>

Moltres employs fully implicit coupling between the neutronics and
thermal-hydraulics governing equations, to fully account for the tightly
coupled physics expected in MSRs due to the movement of fuel in the salt. We
implemented flow using the Navier-Stokes equations and zeroth-order
approximation of eddy viscosity for a more accurate representation of the flow
profile compared to imposing a predetermined velocity field.

The main objective of this thesis is to demonstrate Moltres' capabilities in
modeling multiphysics, steady-state and transient behavior of fast-spectrum
\glspl{MSR} through the study of the \gls{MSFR} concept. This is achieved by
first verifying Moltres' neutronics results against Serpent in the context of
the \gls{MSFR}, and then comparing the coupled neutronics/thermal-hydraulics
steady-state and transient accident results of the \gls{MSFR} concept. The
multiphysics results are verified against the results by Fiorina et al.
\cite{fiorina_modelling_2014} and Aufiero et al.
\cite{aufiero_development_2014}.

\section{Thesis Outline}

The outline of this thesis is as follows: Chapter 2 discusses the history and
features of \glspl{MSR}. The \gls{MSFR} concept is covered in greater detail.
Chapter 3 details the simulation codes and the general modeling approach for
generating the results in this thesis. Chapter 4 provides a neutronics
assessment by comparing key neutronics parameters from Moltres' eigenvalue
calculations to Serpent's Monte Carlo calculations. Chapter 5 presents
steady-state results of coupled neutronics/thermal-hydraulics \gls{MSFR}
simulations in Moltres. Chapters 6 to 9 present transient accident simulation
results for unprotected reactivity insertions, unprotected loss of flow,
unprotected pump overspeed, and unprotected loss of heat sink, respectively.
Lastly, Chapter 10 summarizes the key findings of this thesis and posits some
potential avenues for future work.

### 2020-04-13 model.tex
Completed first draft of Chapters 1-4 for review

The main simulation tool used in this work for studying the \gls{MSFR} is
Moltres. While we used Moltres for the steady-state and transient analysis, it
requires a dedicated neutron transport solver such as Serpent 2 to generate
neutron energy group constant data for the multigroup neutron diffusion
calculations in Moltres. This chapter provides brief introductions of the
Serpent and Moltres codes, and the modeling approach for the multiphysics
simulations.

@@

As mentioned in the previous chapter, we divided the fuel salt loop into two
regions, the central core region where most of the fissions take place, and
the outer loop region where the heat exchanger is located. The central core
region specifically refers to the central region indicated by
the red box in Figure \ref{fig:core}. We simplified the outer loop
into a 1-D pipe as it is a subcritical region and its main purposes are to
introduce a out-of-core residence time for the \glspl{DNP} and to cool the
fuel salt before redirecting it back into the central core region.
Accordingly, this section provides separate descriptions for the governing
equations in the central core region and the outer loop region. There is also
a third region comprising of the blanket salt, the Ni-alloy reflectors, 
and other material . This region is important for capturing an accurate
estimate of neutron leakage as opposed to simpler approximations such as
imposing fixed albedo boundary conditions on the neutron fluxes.

@@

\subsubsection{Neutronics}

@@

While the limitations of the multigroup neutron diffusion compared to other
deterministic and Monte Carlo methods, particularly for flux values near
boundaries, are well-documented, the diffusion model provides acceptable
accuracy at lower computational costs. Moreover, the
\gls{MSFR} contains no material interfaces in the middle of the core where
most of the fission interactions take place. The Results* section provides a
comparison of the \gls{MSFR} multiplication factor values and reactivity
coefficients between Moltres and Serpent.

@@

We assumed $Sc_t = 0.85$ for a fair comparison with the Polimi/TUDelft
models which used the same value. Moltres also accounts for the decay of
\glspl{DNP} outside the active core region by simulating its flow in a
separate 1-D pipe geometry. This outer loop pipe simulation is loosely coupled
to the active core simulation through MOOSE's MultiApp functionality and
inlet/outlet boundary values. The loose coupling is justified as the evolution
of \gls{DNP} concentrations due to inflow is relatively slow. The length and
velocity defined in this geometry may differ according to reactor
specifications. For this work with the \gls{MSFR} model, we assumed a pipe
length of 2.255 m with salt flowing at 1.1275 m s$^{-1}$ for an out-of-core
residence time of 2 seconds to follow the design specifications.

@@

For this work, we have six neutron energy groups according to the energy
boundaries in table \ref{table:bound}, eight \gls{DNP} groups as defined by
the JEFF-3.1.2 library, and the spline interpolation method. The neutron flux
and \gls{DNP} concentration values were approximated by first-order Lagrange
and constant monomial shape functions respectively on the finite element mesh.
Figure * shows the mesh adopted for the \gls{MSFR} model.
We assumed vacuum boundary conditions for all six neutron group fluxes along
the external boundaries of the geometry, and homogeneous Neumann boundary
conditions along the axial symmetry boundary. For the \gls{DNP}
concentrations, we imposed homogeneous Neumann boundary conditions on the
walls, and inflow and outflow boundary conditions on the inlet and outlet
boundaries respectively. The inlet \gls{DNP} concentration values were
imported from the outlet values of the 1-D outer loop pipe at the same
timestep.

@@

For the decay heat model, a previous study on the MSFR by Aufiero et al.
\cite{aufiero_extended_2013} has shown that using three decay heat precursor
groups with different half-lives in the form of exponential equations, can
accurately model decay heat in the MSFR for up to 300 seconds after shutdown
with a relative error of less than 2\%. Thus, we implemented a decay heat
model using the following equation:
%
\begin{align}
	\frac{\partial \omega_k}{\partial t} &= f_k \sum^G_{g=1} \epsilon_{g}
	\Sigma^f_{g} \phi_{g} - \lambda^k \omega_k - \boldsymbol{u} \cdot \nabla
	\omega_k + \nabla \cdot D_t \nabla \omega_k, \label{eq:decayheat} \\
	\intertext{where}
    \omega_k &= \text{total decay heat power density from decay heat
    precursors in group $k$ [W cm$^{-3}$]} \nonumber \\
	f_k &= \text{fraction of decay heat to total power at steady state}
	\nonumber \\
	\epsilon_g &= \text{average fission energy per fission [W]} \nonumber \\
	\lambda^k &= \text{average decay constant of decay heat precursors in
	group $k$ [s$^{-1}$].} \nonumber
\end{align}

@@

\subsubsection{Thermal-Hydraulics}

@@

The flow rate is dictated by an inflow boundary condition at the core inlet
for a volumetric flow rate of 4.5 m$^3$ s$^{-1}$. We imposed no-slip boundary
conditions on the walls of the core, and homogeneous Neumann boundary
conditions on the core outlet. The energy balance equation for temperature is
given in Eq. \ref{eq:temp}. The diffusion term includes turbulent heat
diffusivity based on the eddy viscosity $\mu_t$ and the turbulent Prandtl
number $Pr_t$, which we assume to be equal to 0.85. 
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p \boldsymbol{u}
    \cdot \nabla T + \nabla \cdot [(k + k_t) \nabla T] + Q_s - Q_{hx}
    \label{eq:temp} \\
    k_t &= \frac{\mu_t}{\rho Pr_t} \\
    Q_s &= \Big( 1 - \sum^K_{k=1} f_k \Big) \sum^G_{g=1} \epsilon_g \Sigma_g^f
    \phi_g + \sum^K_{k=1} \omega_k, \label{eq:source}
    \intertext{where}
    c_p &= \text{specific heat capacity of molten salt [J kg$^{-1}$ K$^{-1}$],
    } \nonumber \\
    T &= \text{temperature of molten salt [K]} \nonumber \\
    \boldsymbol{u} &= \text{velocity of molten salt [m s$^{-1}$],} \nonumber
    \\
    k &= \text{thermal conductivity of molten salt [W m$^{-1}$ K$^{-1}$,}
    \nonumber \\
    Q_{hx} &= \text{heat loss rate through the heat exchanger [W].} \nonumber
\end{align}
%
where $K$ is the total number of decay heat groups. The first term in the heat
source expression represents prompt fission heat, and the second term
represents decay heat from the $K$ decay heat groups.

We modeled the heat exchanger using a point source/sink at the center of the
1-D outer loop pipe region. The rate of heat extraction is equivalent to the
nominal 3 GW$_{\text{th}}$ power output with appropriate scaling to account
for the 1-D geometry. *** include more detail when finalized ***

@@

\subsubsection{Neutronics}

\subsubsection{Thermal-Hydraulics}

>>>>

The main simulation tool used in this work for studying the \gls{MSFR} is
Moltres. While we used Moltres for the steady-state and transient analysis, it
requires a dedicated neutron transport solver such as Serpent 2 to generate
neutron energy group constant data for the multigroup neutron diffusion
calculations in Moltres. This chapter provides brief introductions of the
Serpent and Moltres codes, and the general modeling approach for the
multiphysics simulations in Moltres.

@@

As mentioned in the previous chapter, we divided the fuel salt loop into two
regions, the central core region where most of the fissions take place, and
the outer loop region where the heat exchanger is located. The central core
region specifically refers to the central region indicated by
the red box in Figure \ref{fig:core}. We simplified the outer loop
into a 1-D pipe as it is a subcritical region and its main purposes are: to
introduce a out-of-core residence time for the \glspl{DNP}, and to site the
heat exchanger-equivalent object in Moltres.
Accordingly, this section provides separate descriptions for the governing
equations in the central core region and the outer loop region. There is also
a third region comprising of the blanket salt, the Ni-alloy reflectors, 
and other material . This region is important for capturing an accurate
estimate of neutron leakage as opposed to simpler approximations such as
imposing fixed albedo boundary conditions on the neutron fluxes.

@@

\subsubsection{Neutronics Model}

@@

While the limitations of the multigroup neutron diffusion compared to other
deterministic and Monte Carlo methods, particularly for flux values near
boundaries, are well-documented, the diffusion model provides acceptable
accuracy at lower computational costs. Moreover, the central core region
contains no material interfaces except at its boundaries. The Neutronics
results section provides a comparison of the \gls{MSFR} multiplication factor
values and reactivity coefficients between Moltres and Serpent.

@@

We assumed $Sc_t = 0.85$ for a fair comparison with the Polimi/TUDelft
models which used the same value.

\begin{figure}[htb!]
    \centering
    \includegraphics[width=.8\textwidth]{mesh}
    \caption{Mesh adopted in Moltres and a close-up view of the mesh around
    the boron carbide absorber.}
    \label{fig:mesh}
\end{figure}

@@

@@

For this work, we have six neutron energy groups according to the energy
boundaries in table \ref{table:bound}, eight \gls{DNP} groups as defined by
the JEFF-3.1.2 library, and the spline interpolation method. The neutron flux
and \gls{DNP} concentration values were approximated by first-order Lagrange
and constant monomial shape functions respectively on the finite element mesh.
Figure \ref{fig:mesh} shows the mesh adopted for the \gls{MSFR} model.
We assumed vacuum boundary conditions for all six neutron group fluxes along
the external boundaries of the geometry, and homogeneous Neumann boundary
conditions along the axial symmetry boundary. For the \gls{DNP}
concentrations, we imposed homogeneous Neumann boundary conditions on the
walls, and inflow and outflow boundary conditions on the inlet and outlet
boundaries respectively. The inlet \gls{DNP} concentration values were
imported from the outlet values of the 1-D outer loop pipe at the same
timestep.

For the decay heat model, a previous study on the MSFR by Aufiero et al.
\cite{aufiero_extended_2013} had shown that using three decay heat precursor
groups with different half-lives in the form of exponential equations, can
accurately model decay heat in the MSFR for up to 300 seconds after shutdown
with a relative error of less than 2\%. Thus, we implemented a decay heat
model using the following equation:
%
\begin{align}
	\frac{\partial \omega_k}{\partial t} &= f_k \sum^G_{g=1} \epsilon_{g}
	\Sigma^f_{g} \phi_{g} - \lambda^k \omega_k - \boldsymbol{u} \cdot \nabla
	\omega_k + \nabla \cdot D_t \nabla \omega_k, \label{eq:decayheat} \\
	\intertext{where}
    \omega_k &= \text{total decay heat power density from decay heat
    precursors in group $k$ [W cm$^{-3}$]} \nonumber \\
	f_k &= \text{fraction of decay heat to total power at steady state}
	\nonumber \\
	\epsilon_g &= \text{average fission energy per fission [W]} \nonumber \\
	\lambda^k &= \text{average decay constant of decay heat precursors in
	group $k$ [s$^{-1}$].} \nonumber
\end{align}

@@

\subsubsection{Thermal-Hydraulics Model}

@@

The energy balance equation for temperature is
given in Eq. \ref{eq:temp}. The diffusion term includes turbulent heat
diffusivity based on the eddy viscosity $\mu_t$ and the turbulent Prandtl
number $Pr_t$, which we assume to be equal to 0.85. 
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p \boldsymbol{u}
    \cdot \nabla T + \nabla \cdot [(k + k_t) \nabla T] + Q_s
    \label{eq:temp} \\
    k_t &= \frac{\mu_t}{\rho Pr_t} \\
    Q_s &= \Big( 1 - \sum^K_{k=1} f_k \Big) \sum^G_{g=1} \epsilon_g \Sigma_g^f
    \phi_g + \sum^K_{k=1} \omega_k, \label{eq:source}
    \intertext{where}
    c_p &= \text{specific heat capacity of molten salt [J kg$^{-1}$ K$^{-1}$],
    } \nonumber \\
    T &= \text{temperature of molten salt [K]} \nonumber \\
    \boldsymbol{u} &= \text{velocity of molten salt [m s$^{-1}$],} \nonumber
    \\
    k &= \text{thermal conductivity of molten salt [W m$^{-1}$ K$^{-1}$],}
    \nonumber \\
    K &= \text{total number of decay heat groups.} \nonumber
\end{align}
%
The first term in the heat source $Q_s$ represents prompt fission heat, and
the second term represents decay heat from the $K$ decay heat groups.

@@

Moltres also accounts for the decay of
\glspl{DNP} outside the central core region by simulating its flow in a
separate 1-D pipe geometry. This outer loop pipe simulation is implicitly
coupled to the active core simulation through Picard iterations in MOOSE's
MultiApp functionality and inlet/outlet boundary values. For this work with
the \gls{MSFR} model, we assumed a pipe
length of 2.255 m with salt flowing at 1.1275 m s$^{-1}$ for an average
out-of-core residence time of 2 seconds to follow the design specifications.

\subsubsection{Neutronics Model}

Since this region is largely subcritical, the only significant
neutronics-related phenomena are the drift, and decay of \glspl{DNP}.
The governing equation for the \glspl{DNP} is:
%
\begin{align}
    \frac{\partial C_i}{\partial t} &= - \lambda_i C_i - u
    \frac{\partial C_i}{\partial x} + D_t \frac{\partial^2 C_i}{\partial x^2}.
    \label{eq:dnploop}
\end{align}
%
Equation \ref{eq:dnploop} is derived from equation \ref{eq:dnp} by removing
the fission \gls{DNP} source term, and the conversion of the advection and
diffusion terms to their 1-D forms. The decay constants and diffusion
coefficient are the same values used in the central core region.

\subsubsection{Thermal-Hydraulics Model}

Instead of the Navier-Stokes equations, we have a predetermined velocity of
1.1275 m s$^{-1}$ in the outer loop region. The governing equation for
temperature, derived from equation \ref{eq:temp}, is:
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p u
    \frac{\partial T}{\partial x} - Q_{hx} \label{eq:temploop} \\
    Q_{hx} &= \alpha (T - T_i) \delta (x_0) \label{eq:hx} \\
    \intertext{where}
    \alpha &= \text{heat transfer coefficient [W K$^{-1}$],} \nonumber \\
    x_0 &= \text{position of the point heat exchanger [m].} \nonumber
\end{align}

The fission heat source term is replaced with a heat exchanger sink term
which depends on the temperature difference between the fuel salt $T$ and the
secondary loop salt $T_s$. For simplicity, we assumed a constant temperature
of 823 K in the secondary loop. The heat transfer coefficient was determined
by assuming that the fuel outlet temperature is 1023 K and calculating the
heat removal rate to induce a 100 K drop at the given volumetric flow rate
and heat capacity of the fuel salt. We opted to ignore the diffusion term due
to the discontinuity of the temperature distribution across the point heat
exchanger.

\subsection{Boundary Conditions and Flow Transfers}

This subsection details the various boundary conditions for all of the
tracked variables, and the \gls{DNP} and temperature flow transfers between
the central core and outer loop regions.

Starting with the central core region, for the neutron group fluxes, we
imposed vacuum boundary conditions on the
outermost boundaries of the geometry in Figure \ref{fig:core} excluding the
axial boundary. The \gls{DNP} variables have homogeneous Neumann boundary
conditions along the axis and the walls in the central core region, and inflow
and outflow boundary conditions on the inlet and outlet boundaries,
respectively. The temperature variable shares the same type of boundary
conditions as the \gls{DNP} variables.

The flow rate is dictated by an inflow boundary condition at the core inlet
for a volumetric flow rate of 4.5 m$^3$ s$^{-1}$. We imposed no-slip boundary
conditions on the walls of the central core, and homogeneous Neumann boundary
conditions on the outlet. Along the axial boundary, we have homogeneous
Dirichlet boundary condition for the radial velocity component, and
homogeneous Neumann boundary condition for the axial velocity component.

At every timestep, Moltres also calculates weighted averages of the
temperature and \gls{DNP} at the outlet. These values are weighted by the
outflow velocity values at the outlet according to the following equation:
%
\begin{align}
    \overline{\phi} &= \frac{\int_\mathcal{C} \phi(y) u(y) dy}{
    \int_\mathcal{C} u(y) dy} \\
    \intertext{where}
    \phi &= \text{variable to be weighted} \nonumber \\
    \mathcal{C} &= \text{outlet boundary curve} \nonumber \\
    u &= \text{outflow velocity perpendicular to the outlet boundary [m
    s$^{-1}$].} \nonumber
\end{align}

This outflow value from the central core region is transferred to the 1-D
outer loop region as input for the inhomogeneous Dirichlet boundary
condition at the inlet boundary. Likewise, the outflow value from the outer
loop region is used for the inflow value in the central core region. No
averaging is required for this step as the outer loop region is a 1-D system.
We assume that the inflow temperature and \gls{DNP} are uniform at the inlet.
The Picard iterations within every timestep ensure that the two systems are
implicitly coupled even though they're solved separately.

### 2020-04-13 neutronics.tex
Completed first draft of Chapters 1-4 for review

This chapter discusses three main sets of simulation results. First, we
compare the key neutronics results between Serpent and Moltres for a static
model of the \gls{MSFR}, i.e. no salt flow, to assess the accuracy of the
six-group neutron diffusion model in Moltres on a fast-spectrum reactor. This
exercise also serves as a checking exercise for the group constant data
generated for Moltres from Serpent. Second, we present steady-state results
from Moltres with salt flow and verify it against published results, namely
from the Polimi/TUDelft and OpenFOAM models developed by Fiorina et al.
\cite{fiorina_modelling_2014} and Aufiero et al.
\cite{aufiero_development_2014}, respectively. Lastly, we present and compare
transient simulation results from Moltres with the aforementioned models.
Transient accident scenarios include an unprotected reactivity insertion, an
unprotected loss of flow, an unprotected loss of heat sink, a chilled inlet,
and a pump overspeed scenario.

\section{Static Model}

@@

\begin{table}[htb!]
	\centering
	\caption{$\beta_{\text{eff}}$ values from Serpent and Moltres at 973 K.}
	\begin{tabular}{l S S}
		\toprule
		{Code} & {$\beta_{\text{eff}}$ [pcm]} & {Difference wrt Serpent [pcm]}
		\\
		\midrule
		{Serpent} & 304.08 \pm .81 & {-}\\
		{Moltres} & 301.19 \pm .20 & 2.89\\
		\bottomrule
	\end{tabular}
	\label{table:betaeff}
\end{table}
%
\begin{figure}[htb!]
    \centering
    \includegraphics[width=.8\textwidth]{reactivity}
    \caption{Reactivity values from Serpent and Moltres. The Doppler
    reactivity values were calculated at a fixed density of 4.1249 g
    cm$^{-3}$. The density reactivity values were calculated at a fixed
    temperature of 973 K.}
    \label{fig:reactivity}
\end{figure}
%
\begin{table}[htb!]
	\centering
	\caption{Doppler, density, and total temperature coefficients
	for the temperature range of 800 K to 1400 K.}
	\begin{tabular}{l S S S S}
		\toprule
		{Code} & {$\alpha_D$ (log) [pcm]} & {$\alpha_D$ (linear) [pcm
		K$^{-1}$]} & {$\alpha_\rho$ [pcm K$^{-1}$]} & {$\alpha_T$ [pcm
		K$^{-1}$]} \\
		\midrule
		{Serpent} & -4034 \pm 14 & 3.737 \pm 0.013 & 3.424 \pm 0.013 & 7.165
		\pm 0.013 \\
		{Moltres} & {-} & {-} & {-} & 7.184\\
		\bottomrule
	\end{tabular}
	\label{table:alpha}
\end{table}

@@

@@

\section{Steady-State Results}

With the verification of Moltres' neutronics modeling capabilities in the
context of the \gls{MSFR}, we now move on to the multiphysics simulation
results. This section covers the steady-state multiphysics results from
Moltres.

The procedure for obtaining the steady-state results involved several steps
due to the highly coupled \glspl{PDE}. First, we ran a preliminary transient
simulation of fluid flow in the \gls{MSFR} core, starting from zero inlet
velocity and gradually ramping it up to match the nominal flow rate (4.5 m$^3$
s$^{-1}$); otherwise Moltres had difficulty converging to the desired fully
developed flow profile. We imposed a parabolic flow profile at the inlet.
Next, we imported these fully developed flow values as initial values for
velocity in the actual transient simulation modeling the full coupled
neutronics and thermal-hydraulics. The initial values for the temperature and
neutron group flux distributions are 953 K and $1 \times 10^{14}$ cm$^{-2}$
s$^{-1}$ uniformly throughout the geometry. Finally, we assume that steady
state is reached when the volume integral values of every variable remain
constant (up to 6 sig. fig.) for at least four seconds in the simulation; this
time period corresponds to the nominal circulation time of the \gls{MSFR}.

For a direct comparison with the steady-state results from the Polimi/TUDelft
models, the bulk of our steady-state results do not have decay heat modeling.
Instead, we separately discuss the minor differences borne from decay heat
modeling in the last subsection.

\subsection{Thermal-Hydraulics}

Figure \ref{fig:flow-temp} shows the temperature and velocity fields
of the fuel salt in the core at steady state from Moltres and the
Polimi/TUDelft models. The results from Moltres show good qualitative
agreement with the Polimi/TUDelft models; we observe similar flow and hotspot
features in all three models. There is a large recirculation region near the
blanket tank walls arising from turbulent flow. Inertial forces dominate over
viscous forces to form this large eddy. The figure also shows two relatively
stagnant regions along the central axis at the top and bottom of the core.
Temperature hotspots form in these regions of recirculation as convection is
the dominant heat transfer mechanism. The maximum temperature from Moltres,
1279 K near the bottom of the recirculation zone, is closer to the maximum
temperature in the Polimi model ($\approx$ 1300 K) than the TUDelft model
($\approx$ 1200K). The minimum temperature is 922 K at the inlet. Figure
\ref{fig:flow} provides an alternate view of the flow profile through flow
streamlines superimposed on the velocity magnitude distribution. The fastest
salt flow occurs at the inlet, outlet, and at core half-height approximately
0.40 m away from the central axis.

\begin{figure}[htb!]
    \centering
    \begin{subfigure}[t]{.37\textwidth}
        \centering
        \includegraphics[width=\textwidth]{flow-temp}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.625\textwidth}
        \centering
        \includegraphics[width=\textwidth]{flow-temp-fiorina}
    \end{subfigure}
    \caption{Temperature and velocity fields in the core from Moltres
    (left), Polimi (center), and TUDelft (right) models.}
    \label{fig:flow-temp}
\end{figure}

\begin{figure}[htb!]
    \centering
    \includegraphics[width=.6\textwidth]{flow}
    \caption{Fuel salt flow streamlines and velocity magnitude in the core.}
    \label{fig:flow}
\end{figure}

While the temperatures at the hotspots are well below the melting point of the
Ni-alloy structure (1500 K), they may cause undue thermal stress on the
blanket tank structure and induce relatively faster salt corrosion rates. A
sudden, large reactivity insertion could push fuel salt temperatures above the
melting point of the Ni-alloy and cause irreversible damage. Furthermore,
the reservoir of hot fuel salt may cause unpredictable behavior during
transient scenarios when the flow profile undergoes a drastic change.
Thus, Rouch et al. \cite{rouch_preliminary_2014} developed an improved
hourglass-shaped design to optimize flow distribution and prevent these
recirculation zones and hotspots from forming. A study of this new design
using Moltres is a potential subject for future work when a proper turbulence
model is in place.

\subsection{Neutronics}

\subsection{Decay Heat}

A decay heat model effectively redistributes a fraction of the heat source
from the center of the core to the entire loop. Thus, we expect to observe
a slight flattening of the temperature distribution across the entire primary
loop.

\section{Transient Results}

As noted by Fiorina et al. \cite{fiorina_modelling_2014}, explicit decay heat
modeling has a negligible effect on reactivity-, pump-, and enchanced
cooling-driven transients. The Polimi model presented results with the decay
heat model for the loss of heat sink transient scenario only. For a fair
comparison, we also

\subsection{Unprotected Reactivity Insertion}

\subsection{Unprotected Loss of Flow}

\subsection{Unprotected Pump Overspeed}

\subsection{Unprotected Loss of Heat Sink}

\subsection{Unprotected Chilled Inlet}

>>>>

In this chapter, we compare key neutronics results between Serpent and Moltres
for a static model of the \gls{MSFR}, i.e. no salt flow, and uniform
temperature distribution to assess the accuracy of the
six-group neutron diffusion model in Moltres on a fast-spectrum reactor. This
exercise also serves as a verification for the group constant data
generated for Moltres from Serpent.

\section{Effective Multiplication Factor and Delayed Neutron Fraction}

@@

\begin{table}[htb!]
	\centering
	\caption{$\beta_{\text{eff}}$ values from Serpent and Moltres at 973 K.}
	\begin{tabular}{l S S}
		\toprule
		{Code} & {$\beta_{\text{eff}}$ [pcm]} & {Difference wrt Serpent [pcm]}
		\\
		\midrule
		{Serpent} & 304.08 \pm .81 & {-}\\
		{Moltres} & 301.19 \pm .20 & 2.89\\
		\bottomrule
	\end{tabular}
	\label{table:betaeff}
\end{table}

\section{Reactivity Feedback Coefficients}

@@

\begin{figure}[htb!]
    \centering
    \includegraphics[width=.8\textwidth]{reactivity}
    \caption{Reactivity values from Serpent and Moltres. The Doppler
    reactivity values were calculated at a fixed density of 4.1249 g
    cm$^{-3}$. The density reactivity values were calculated at a fixed
    temperature of 973 K.}
    \label{fig:reactivity}
\end{figure}
%
\begin{table}[htb!]
	\centering
	\caption{Doppler, density, and total temperature coefficients
	for the temperature range of 800 K to 1400 K.}
	\begin{tabular}{l S S S S}
		\toprule
		{Code} & {$\alpha_D$ (log) [pcm]} & {$\alpha_D$ (linear) [pcm
		K$^{-1}$]} & {$\alpha_\rho$ [pcm K$^{-1}$]} & {$\alpha_T$ [pcm
		K$^{-1}$]} \\
		\midrule
		{Serpent} & -4034 \pm 14 & 3.737 \pm 0.013 & 3.424 \pm 0.013 & 7.165
		\pm 0.013 \\
		{Moltres} & {-} & {-} & {-} & 7.184\\
		\bottomrule
	\end{tabular}
	\label{table:alpha}
\end{table}

\section{Neutron Energy Spectrum}

@@
